\documentclass[twocolumn]{article}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{graphicx}
\graphicspath{ {./images/} }

%links
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

%Pseudocode
\usepackage[german,vlined,longend,ruled,linesnumbered]{algorithm2e}
\SetKw{KwDownTo}{downto}
\SetKw{KwAnd}{and}
\SetKw{KwOr}{or}
\SetKwBlock{DoParallel}{do in parallel}{end}
\usepackage{xcolor}
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}
\DontPrintSemicolon

\newcommand{\aetitle}{Efficient updating Customizable Contraction Hierarchies} % Title of the 

\newcommand{\studentOne}{Marius Hahn} % Name 2
\newcommand{\studentTwo}{Efficient updating Customizable Contraction Hierarchies} % Name 2


% Bis zum 19.07. soll ein kurzer Report abgegeben werden (ca. 2 Seiten), der das zugewiesene
% Thema kritisch betrachtet und Limitation der vorgestellten Algorithmem analysiert, z.B. hinsichtlich 
% der Performanz. Außerdem sollen mögliche auf dem Paper basierende weitergehende Forschungsfragen
% benannt werden.

\begin{document}

\input{assets/title}

\section{Intro}

This is a seminar on "Efficient shortest path index maintenance on dynamic
road networks with theoretical guarantees" \cite{Ouyang2020}. The papers generally is
about finding the shortest path in road networks. By \textit{shortest} it is meant,
the path that requires the less time to get from source $s$ to a target $t$. The route
network is modeled as a directed graph $G(V,E)$ where each street crossing represents a
vertex $v \epsilon V$ and each road between crossings represents an edge $e \epsilon E$.
The most basic and solid method to find shortest paths between vertices in a graph is
Dijkstra's algorithm \cite{Dijkstra1959}. This algorithm is proofed to always return the
correct shortest path but it is not fast for just in time route planning on large
road networks as we know it from services like Google Maps. There are many of
different approaches that try to speed up shortest path queries by precomputing 
any different kind of index structure before doing the shortest path query. The index 
structure discussed in \cite{Ouyang2020} is CH (Contraction Hierarchies)\cite{Geisberger}
with some extension. This extension is CCH (Customizable Contraction Hierarchies) 
\cite{Dibbelt2014}. Although the authors of \cite{Ouyang2020} never mention the term
CCH their approaches builds the same index structure. This is a pity, as for this part 
they kind of reinvent the wheel. 
\\
The difference lies in updating 
the CCH index structure. For updating the CCH, the authors of \cite{Ouyang2020} will use yet another
index structure called \textit{SS-Graph} that help to exactly identify the shortcuts that
have to be updated, after some edge weight has changed. In todays implementation, the whole
index structure is recomputed periodically. This is an valid approach as it is fast enough 
to stay accurate for route planning in road networks.
\\
In \cite{Ouyang2020} the authors would like to find a way that make it possible to handle streaming
updates. Therefore it is necessary to handle streaming updates, meaning handle single weight decrease
and increases. To handle this another index structure the \textit{SS-Graph} is introduced.
This index structure is basically a helper structure to identify the shortcuts
that have to be updated in the CCH. 
\\
The disadvantage of this \textit{SS-Graph} is that the overall space consumption rises.
In their own test by a factor of 12.7, which can be a deal breaker for large networks.
Finally they introduce a way to create the necessary \textit{SS-Graph} on the fly. Which 
is only a part of the whole structure. 
Sadly the exact way, how, is missing in the paper \cite{Ouyang2020}.


\newpage
\bibliographystyle{plain}
\bibliography{assets/references}

\end{document}
